Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
polishing section of methodology

We group buildings which will be too close at time $t$
and aggregate the buildings in the same group by introducing bridges.
We grow the buildings by buffering with miter joins.
Our building simplification consists of two steps.
The first one is to use dilation and erosion to remove pits and spikes.
The second step is to remove vertices using Imai--Iri algorithm.
To make sure that the intermediate-scale buildings never shrink,
we merge the shape of a building with the shape at the previously immediate 
step. 
Also, we clip the building using the shape on goal map.

\subsection{Grouping buildings based on buffering}
\label{sec:Group}
There are many ways to group buildings.

Using MST to group buildings: \citet{Zhang2013, 
	Cetinkaya2015,Deng2017,Regnauld1996}

We group buildings based on their buffers
(see \fig\ref{fig:RemoveBay} for example).
We wish to remove some ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may appear after some buildings are merged by bridging
(see for example \fig\ref{fig:RemoveBay}e).
To remove such kind of bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
The result of having removed a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{RemoveBay}
	\caption{Group buildings iteratively.
		(a) Original buildings.
		(b) Dilate each building in (a) with distance $\dtrm{G}+\dtrm{D}$.		
		(c) Erode the polygons in (b) with distance $\dtrm{D}$.
		(d) Dilate the polygons in (c) with distance 
		$\frac{\sqrt{5}}{2} d_{\epsilon,t}$. 
		If two polygons in (d) intersect, 
		the original buildings in (a) will be put in the same group 
		because they will become too close at time $t$.
		Until this step, there two groups according to (d), 
		one consists of the single middle building and 
		the other group consists of the surrounding $9$ buildings.
		(e) The result of growing and merging at time $t$ 
		if we use $\dtrm{D}=0$.
		The process of (f), (g), and (h) is similar to 
		that of (b), (c), and (d).		
		The difference is that 
		instead of applying the operators to each single building, 
		we do that for the buildings in the same group.
		In (f), we manage to remove the bay in (e) by additionally dilating 
		with distance $\dtrm{D}$.
		There is only one group left according to (h).
		We iteratively group buildings in this way until the number of groups 
		does not decrease.
	}
	%in this example, we used _dblTotalGrow *= 5;
	\label{fig:RemoveBay}
\end{figure*}

@@

\subsection{Growing buildings based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G} (\alpha \ge 1)$, 
where $d_\mathrm{G}$ is the growing distance, 
away from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

We denote by $d_\mathrm{G}$ the total growth. The growth at time $t$ is
\begin{equation}
	\label{eq:d_Gt}
	\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}

\subsection{Simplifying grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \citet{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes
(see \fig\ref{fig:RemovePitAndSpike}).

At time $t$, we grow buildings with distance $\dtrm{G}$,
dilate with distance $\dtrm{D} (\dtrm{D}>0)$,
erode with distance $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
and dilate back with distance $\dtrm{E}$.
A problem we may have is that we may break a building by eroding.
The reason is that 
some parts of a building may be increased (by growing and dilating) 
with distance $\dtrm{G}+\dtrm{D}$, 
but be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
If  $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
and a building is not thick enough, 
the building may be broken into several parts
(see \fig\ref{fig:ErosionBreak}).
In order to avoid this problem, we require that
\[
\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
\]
which means
\begin{equation}
\label{eq:d_Dt}
\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\end{equation}

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$
(see \eq\ref{eq:d_epsilont}) so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, which was used as a length threshold by 
\citet{Regnauld2001,Li2004,Basaraner2008}.
Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we use
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-l} S_s.
\end{equation}

We wish to remove ``bays'' which have ``widths'' less than $2\sqrt{a_h/\pi}$.
\todo{why? more details}
Usually, our $\dtrm{D}$ is not large enough to do so.
We use the upper bound in \eq\ref{eq:d_Dt}, that is,
\[
\dtrm{D} = \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\]

>>>>

We find buildings which will be too close at time $t$
and aggregate the buildings in the same group by introducing bridges.
We grow the (bridged) original buildings by buffering with miter joins.
Our building simplification consists of two steps.
The first one is to use dilation and erosion to remove pits and spikes.
The second step is to remove vertices using Imai--Iri algorithm.
To make sure that the intermediate-scale buildings never shrink,
we merge the shape of a building 
with the shape at the previously immediate step. 
Also, we clip the building using the shape on goal map.

Our aggregation is based on growing and some of simplifying. 
So we present the two operators before aggregating.

\subsection{Growing buildings based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering a polygon, i.e.,
one with round joins and the other with miter joins 
(see \fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way to
better preserve the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}a).
To avoid this kind of interruptions, 
we require that if a vertex of the 
buffer is more than $\alpha \dtrm{G} (\alpha \ge 1)$
away from the original vertex, 
a \emph{square} join is applied
(see \fig\ref{fig:Buffer_MiterLimits}b).
Distance $\dtrm{G}$ is the growth at time $t$.
We denote by $d_\mathrm{G}$ the growth for goal map.
Then we define
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square join is applied when an angle is 
smaller (more acute) than $83.6 \degree$.

\subsection{Simplifying grown buildings}
\label{sec:Simplify}
\citet{Damen2008} generalized buildings using morphological operators.
A drawback of this method is that the directions of the buildings have to be 
concerned.
\citet{Meijers2016} simplified buildings 
based on offset curves generated from straight skeletons.
We use a method based on buffering to remove pits and spikes of buildings.
Our method is slightly different than \citet{Meijers2016},
but there is an available library \textsc{Clipper} \citep{Johnson2014} 
for the operations.
\fig\ref{fig:RemovePitAndSpike} illustrates our buffering-based method.
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.

At time $t$, we grow buildings with distance $\dtrm{G}$,
dilate with distance $\dtrm{D} (\dtrm{D}>0)$,
erode with distance $\dtrm{D}+\dtrm{E} (\dtrm{E}>0)$,
and dilate back with distance $\dtrm{E}$.
A problem we may have is that 
a building may be broken by eroding
(see \fig\ref{fig:ErosionBreak} for example).
The reason is that 
some parts of a building may be increased (by growing and dilating) 
with distance $\dtrm{G}+\dtrm{D}$, 
but can be decreased (by eroding) as much as $\alpha (\dtrm{D}+\dtrm{E})$.
If $\dtrm{G}+\dtrm{D} < \alpha (\dtrm{D}+\dtrm{E})$ 
and the building is not thick enough, 
the thin part may disappear.
In order to avoid this problem, we require that
\[
\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
\]
which means
\begin{equation}
\label{eq:d_Dt}
\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\end{equation}

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$ so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, 
which was used as a length threshold by, for example, 
\citet{Regnauld2001}.
Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we use
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
%Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
%$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
%t \cdot \frac{l}{2} M_\mathrm{g} >0$.
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot d_\mathrm{G} - t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} < \frac{2 d_\mathrm{G}}{l}.
\end{equation}

We wish to remove ``bays'' 
which have ``widths'' less than $r_\mathrm{h} = 2\sqrt{a_\mathrm{h}/\pi}$.
Variable $a_\mathrm{h}$ is the least area for a hole to be presented on map.
Following \citep{Chaudhry2008}, we set $a_\mathrm{h} = 8\,\mathrm{mm}^2$.
Variable $r_\mathrm{h}$ is the radius of such a hole 
supposing that the hole is a circle.
Sometimes, our $\dtrm{D}$ is not large enough to do so 
because of the limitation from \eq\ref{eq:d_Dt}.
We define
\[
\dtrm{D} =\min (\frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}, r_\mathrm{h} M_t) .
\]

\subsection{Grouping buildings based on buffering}
\label{sec:Group}
%There are many ways to group buildings.
%
%Using MST to group buildings: \citet{Zhang2013, 
%	Cetinkaya2015,Deng2017,Regnauld1996}

Original buildings grow according to time $t$.
We put the original building in the same group if 
they grow to become too close.
We group buildings based on buffering.
(see \fig\ref{fig:RemoveBay} for example).
We wish to remove some ``bays'' 
which have widths less than $2 \dtrm{D}$.
A bay may appear after some buildings are merged by bridging
(see for example \fig\ref{fig:RemoveBay}e).
To remove such kind of bay,
we overgrow (see \fig\ref{fig:RemoveBay}b and~e) 
and then erode back (see \fig\ref{fig:RemoveBay}c and~f) 
with distance $\dtrm{D}$.
There may be some buildings in a bay (see \fig\ref{fig:RemoveBay}c),
so we iteratively group until the number of groups does not decrease.
The result of having removed a bay is the outer polygon of 
\fig\ref{fig:RemoveBay}h. 
In comparison, the result is \fig\ref{fig:RemoveBay}e 
if we do not remove a bay.
Note that the pit we want to remove in \fig\ref{fig:RemovePitAndSpike} is a 
kind of bay and will be removed by overgrowing.

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{RemoveBay}
	\caption{Group buildings iteratively.
		(a) Original buildings.
		(b) Dilate each original building with distance 
		$\dtrm{G}+\dtrm{D}$.		
		(c) Erode the dilated polygons with distance $\dtrm{D}$.
		(d) Dilate the eroded polygons with distance $\dtrm{C}$. 
		If two polygons in (d) intersect, 
		the original buildings will be put in the same group 
		because they will become too close at time $t$.
		There two groups according to (d).
		One consists of the single middle building and 
		the surrounding $9$ buildings comprise the other group.
		(e) The result of growing and merging at time $t$ 
		if we use $\dtrm{D}=0$.
		The process of (f), (g), and (h) is similar to 
		that of (b), (c), and (d).		
		The difference is that 
		instead of applying the operators to each single building, 
		we do that for the buildings in the same group.
		In (f), we manage to remove the bay in (e) by additionally dilating 
		with distance $\dtrm{D}$.
		There is only one group left according to (h).
		We iteratively group buildings in this way until the number of groups 
		does not decrease.
	}
	%in this example, we used _dblTotalGrow *= 5;
	\label{fig:RemoveBay}
\end{figure*}

@@
